### 2023-06-14 resilience.tex
up

\begin{example}
Let us consider a VASS with only one state $q$, one counter, and one transition that substracts $-1$ from the counter, with $\Safe = \downarrow q(0)$, $\Bad = \uparrow q(1)$,
then resilience hold (one always ends up in the positive integers) but not bounded resilience: for every bound $k$ there is an element of $\Bad$ e.g. $q(-k-1)$ which necessitate at least $k+1$ steps before it can reach $\Safe$. 
\end{example}

These three resilience problems are decidable for finite transition systems but undecidable for (general) infinite-state transition systems. So we restrict our framework to the class of infinite-state WSTS. Since most of decidable properties in WSTS rely on the computation of upward or downward-closed sets \cite{DBLP:journals/iandc/AbdullaCJT00, DBLP:journals/tcs/FinkelS01}, we consider upward-closed or downward-closed sets $\Safe$ and $\Bad$. In \cite{DBLP:journals/corr/abs-2108-00889}, the authors considered that $\Bad$ is downward-closed and $\Safe$ is upward-closed. \mathieu{Remarquer que dans l'example~\ref{Example} on a à la fois upward closed ET downward closed pour $\Safe$ ET $\Bad$.}

Surprinsingly, we have not found decidability results about the resilience problems for WSTS.	
We deduce decidability results for the four pairs of sets $\Safe$ and $\Bad$ downward-closed and upward-closed as seen in Section~\ref{synthesis}.
In particular, the existing proofs of resilience use the decidability of reachability; but we wish to decide resilience for models with undecidable reachability.
%
%	 and ideals are recursive 
Our result will rely on coverability instead of reachability. We moreover show undecidability when coverability is not decidable in the case $\Safe = \uparrow \Safe$
and in the general case when $\Safe = \downarrow \Safe$.

@@

%We first assume that the safety property is given by an upward-closed set and the bad condition by a decidable downward-closed set. 
% \textcolor{red}{Seems like a reasonable assumption to me.}

%From these considerations, we formulate instances of the abstract resilience problems for well-
%structured transition systems.

>>>>

\begin{example}
Let us consider a VASS with only one state $q$, one counter, and one transition that substracts $-1$ from the counter, with $\Safe = \downarrow q(0)$, $\Bad = \uparrow q(1)$,
then resilience hold but not bounded resilience: for every bound $k$ there is an element of $\Bad$ e.g. $q(k+1)$ which necessitate at least $k+1$ steps before it can reach $\Safe$. 
\end{example}

These three resilience problems are decidable for finite transition systems but undecidable for (general) infinite-state transition systems. So we restrict our framework to the class of infinite-state WSTS. Since most of decidable properties in WSTS rely on the computation of upward or downward-closed sets \cite{DBLP:journals/iandc/AbdullaCJT00, DBLP:journals/tcs/FinkelS01}, we consider upward-closed or downward-closed sets $\Safe$ and $\Bad$. In \cite{DBLP:journals/corr/abs-2108-00889}, the authors considered that $\Bad$ is downward-closed and $\Safe$ is upward-closed. %\mathieu{Remarquer que dans l'example~\ref{Example} on a à la fois upward closed ET downward closed pour $\Safe$ ET $\Bad$.} 
Remark that in Example~\ref{Example}, $\Safe$ and $\Bad$ are both upward-closed and downward-closed.

Surprinsingly, we have not found decidability results about the resilience problems for WSTS.	
We deduce decidability results for the four pairs of sets $\Safe$ and $\Bad$ downward-closed and upward-closed as seen in Section~\ref{synthesis}.
In particular, the existing proofs of resilience use the decidability of reachability; but we wish to decide resilience for models with undecidable reachability.
Our result will rely on coverability instead of reachability. We moreover show undecidability when coverability is not decidable in the case $\Safe = \uparrow \Safe$
and in the general case when $\Safe = \downarrow \Safe$.

@@
